ZPY: Open Source Synthetic Data for Computer Vision

### 2021-07-07 docs/paper/paper.tex
better cover image

% https://www.overleaf.com/learn/latex/Inserting_Images
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{cover.png}
	\caption{Synthetic images of a raspberri pi created with zpy: (A) color image, (B) segmentation image, (C) depth image. These images are used to train a deep learning model, which predicts bounding boxes on key components as seen in the (D) prediction image}
	\label{fig:fig1}
\end{figure}

>>>>

% https://www.overleaf.com/learn/latex/Inserting_Images
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{cover.png}
	\caption{Synthetic images of a Raspberry Pi created with zpy: (A) color image, (B) segmentation image, (C) depth image. These images are used to train a deep learning model, which predicts bounding boxes for circuit board components as seen in the (D) prediction image}
	\label{fig:fig1}
\end{figure}
